---
title: "calculate_indices"
author: "Catarina Pien"
date: '2022-10-07'
output: html_document
editor_options: 
  chunk_output_type: console
---
# Load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (!require('tidyverse')) install.packages('tidyverse'); library('tidyverse')
if (!require('patchwork')) install.packages('patchwork'); library('patchwork')
if (!require('lubridate')) install.packages('lubridate'); library('lubridate')
if (!require('odbc')) install.packages('odbc'); library('odbc') # database functions
if (!require('Kendall')) install.packages('Kendall'); library('Kendall')
if (!require('car')) install.packages('car'); library('car')
if (!require('MuMIn')) install.packages('MuMIn'); library('MuMIn')
if (!require('lme4')) install.packages('lme4'); library('lme4')
if (!require('afex')) install.packages('afex'); library('afex')
if (!require('trend')) install.packages('trend'); library('trend')
if (!require('rms')) install.packages('rms'); library('rms')
if (!require('mgcv')) install.packages('mgcv'); library('mgcv')
options(scipen=999) # Getting rid of scientific notation
windowsFonts(Times = windowsFont("Times New Roman"))
```

# Bring in data
```{r}
# read in catch data
data <- readRDS("data_clean/seine_djfmp_ybfmp.rds")
summary(data)

# add year column
data$Year <- format(data$SampleDate, format="%Y")

# read in discharge data from DAYFLOW
## needs updating through 2021, maybe?

Discharge <- 
  read.csv("data/dayflow_1994_2019.csv")
Discharge$Year <- as.factor(Discharge$Year)
Discharge$Mo <- as.factor(Discharge$Mo)

# read in river mile data - Will be used to determine center of distribution 
## needs updating to reflect YBFMP sites and maybe DJFMP data that was filtered out in prior versions?
Site_RM <- 
  read.csv("Data/Site_Coords.csv")

# Need subarea numbers
djfmp_site_file <- contentid::resolve("hash://sha256/f0f9e66da7415df90a7c0ea4c01938ecadd71ad412af1ccc940e861e63e96ba7")
djfmp_sites0 <- read_csv(djfmp_site_file)
```

# Create species datasets
```{r}
# SACPIK Data ---------------------------------------------------------------

data_SACPIK <- 
  data %>% 
  filter(!(is.na(Volume))) %>% # Removing samples without volume data
  select(EventID, Location, RegionCode, StationCode, SampleDate, Year, Month, Jday, IEPFishCode, ForkLength, CountAdj, Volume, DO, WaterTemp, Turbidity, Secchi, SpecificConductance) %>% 
  filter(IEPFishCode == "SACPIK") %>%  # Only keeping catch for SACPIK
  mutate(IEPFishCode = as.character(IEPFishCode))
head(data_SACPIK)
str(data_SACPIK)

# SPLT Data ---------------------------------------------------------------

data_SPLITT <- 
  data %>% 
  filter(!(is.na(Volume))) %>% # Removing samples without volume data
  select(EventID, Location, RegionCode, StationCode, SampleDate, Year, Month, Jday, IEPFishCode, ForkLength, CountAdj, Volume, DO, WaterTemp, Turbidity, Secchi, SpecificConductance) %>% 
  filter(IEPFishCode == "SPLITT") %>%  # Only keeping catch for SACPIK
  mutate(IEPFishCode = as.character(IEPFishCode))
head(data_SPLITT)
str(data_SPLITT)

# SASU Data ---------------------------------------------------------------

data_SACSUC <- 
  data %>% 
  filter(!(is.na(Volume))) %>% # Removing samples without volume data
  select(EventID, Location, RegionCode, StationCode, SampleDate, Year, Month, Jday, IEPFishCode, ForkLength, CountAdj, Volume, DO, WaterTemp, Turbidity, Secchi, SpecificConductance) %>% 
  filter(IEPFishCode == "SACSUC") %>%  # Only keeping catch for SACPIK
  mutate(IEPFishCode = as.character(IEPFishCode))
head(data_SACSUC)
str(data_SACSUC)
```

# Filter species datasets to appropriate months, sizes (Age-0)

```{r}
# SACPIK Data ---------------------------------------------------------------
# Based on length frequency histograms - age 0 make up majority of catch during these months 
# Filter to June + July, >24mm, <61 in June and <71 in July

data_SACPIK_age0 <- data_SACPIK %>%
  filter(Month %in% c(6, 7),
         ForkLength > 24,
         case_when(Month == 6 ~ ForkLength < 61,
                   Month == 7 ~ ForkLength < 71 )) %>%
  mutate(CPUE = CountAdj/Volume,
         Volume_Z = scale(Volume),
         Julian_Z = scale(Jday),
         Julian_Sq_Z = scale(Jday^2),
         Region = as.factor(case_when(RegionCode %in% c(1:5) ~ "Delta",
                                      RegionCode %in% c(6:8) ~ "Sacramento",
                                      RegionCode %in% c(9:10) ~ "San_Joaquin",
                                      grepl("YBFMP", EventID) ~ "Yolo"))) # RegionCode should be subarea. 


# SPLITT Data ---------------------------------------------------------------
# Based on length frequency histograms - age 0 make up majority of catch during these months 
# Filter to May + June, >24mm, <51 in May and <66 in June

data_SPLITT_age0 <- data_SPLITT %>%
  filter(Month %in% c(5,6),
         ForkLength > 24,
         case_when(Month == 5 ~ ForkLength < 50,
                   Month == 6 ~ ForkLength < 61 )) %>%
  mutate(CPUE = CountAdj/Volume,
         Volume_Z = scale(Volume),
         Julian_Z = scale(Jday),
         Julian_Sq_Z = scale(Jday^2),
         Region = as.factor(case_when(RegionCode %in% c(1:5) ~ "Delta",
                                      RegionCode %in% c(6:8) ~ "Sacramento",
                                      RegionCode %in% c(9:10) ~ "San_Joaquin",
                                      grepl("YBFMP", EventID) ~ "Yolo"))) # RegionCode should be subarea. 

# SACSUC --------------------------------------------------------------------
# Based on length frequency histograms - age 0 make up majority of catch during these months 
# Filter to May + June, >24mm, <51 in May and <66 in June
data_SACSUC_age0 <- data_SACSUC %>%
  filter(Month %in% c(5,6, 12),
         ForkLength > 24,
         case_when(Month == 5 ~ ForkLength < 51,
                   Month %in% c(12, 6) ~ ForkLength < 66 )) %>%
  mutate(CPUE = CountAdj/Volume,
         Volume_Z = scale(Volume),
         Julian_Z = scale(Jday),
         Julian_Sq_Z = scale(Jday^2),
         Region = as.factor(case_when(RegionCode %in% c(1:5) ~ "Delta",
                                      RegionCode %in% c(6:8) ~ "Sacramento",
                                      RegionCode %in% c(9:10) ~ "San_Joaquin",
                                      grepl("YBFMP", EventID) ~ "Yolo"))) # RegionCode should be subarea. 


```

# Calculate Regional and System Wide Indices

```{r}
# SACPIK Data ---------------------------------------------------------------
SACPIK_Index_Final <-
  data_SACPIK_age0 %>%
  #filter(subarea != 8) %>%
  group_by(StationCode, Year, Month, Region) %>% 
  summarise(CPUE = mean(CPUE)) %>% 
  group_by(Year, Month, Region) %>% 
  summarise(CPUE = mean(CPUE)) %>% 
  group_by(Year, Region) %>% 
  summarise(CPUE = mean(CPUE)) %>% 
  spread(Region, CPUE)

SACPIK_Index_Final$Delta_Index = SACPIK_Index_Final$Delta
SACPIK_Index_Final$Sacramento_Index = SACPIK_Index_Final$Sacramento
SACPIK_Index_Final$San_Joaquin_Index = SACPIK_Index_Final$San_Joaquin
SACPIK_Index_Final$Watershed_Index = rowSums(SACPIK_Index_Final[,2:4])

SACPIK_Index_Final <- 
  SACPIK_Index_Final[,c(1,5:8)]
head(SACPIK_Index_Final)

#write.csv(SACPIK_Index_Final, "Output/SACPIK_Index_Final.csv", row.names = FALSE)

# SPLITT Data ---------------------------------------------------------------
SPLITT_Index_Final <-
  data_SPLITT_age0 %>%
  #filter(subarea != 8) %>%
  group_by(StationCode, Year, Month, Region) %>% 
  summarise(CPUE = mean(CPUE)) %>% 
  group_by(Year, Month, Region) %>% 
  summarise(CPUE = mean(CPUE)) %>% 
  group_by(Year, Region) %>% 
  summarise(CPUE = mean(CPUE)) %>% 
  spread(Region, CPUE)


SPLITT_Index_Final$Delta_Index = SPLITT_Index_Final$Delta
SPLITT_Index_Final$Sacramento_Index = SPLITT_Index_Final$Sacramento
SPLITT_Index_Final$San_Joaquin_Index = SPLITT_Index_Final$San_Joaquin
SPLITT_Index_Final$Watershed_Index = rowSums(SPLITT_Index_Final[,2:4])

SPLITT_Index_Final <- 
  SPLITT_Index_Final[,c(1,5:8)]
head(SPLITT_Index_Final)

#write.csv(SPLITT_Index_Final, "Output/SPLITT_Index_Final.csv", row.names = FALSE)

# SACSUC Data ---------------------------------------------------------------

SACSUC_Index_Final <-
  data_SACSUC_age0 %>%
  filter(Month != 12) %>% # Removing December
  group_by(StationCode, Year, Month, Region) %>% 
  summarise(CPUE = mean(CPUE)) %>% 
  group_by(Year, Month, Region) %>% 
  summarise(CPUE = mean(CPUE)) %>% 
  group_by(Year, Region) %>% 
  summarise(CPUE = mean(CPUE)) %>% 
  spread(Region, CPUE)


SACSUC_Index_Final$Delta_Index = SACSUC_Index_Final$Delta
SACSUC_Index_Final$Sacramento_Index = SACSUC_Index_Final$Sacramento
SACSUC_Index_Final$San_Joaquin_Index = SACSUC_Index_Final$San_Joaquin
SACSUC_Index_Final$Watershed_Index = rowSums(SACSUC_Index_Final[,2:4])


SACSUC_Index_Final <- 
  SACSUC_Index_Final[,c(1,5:8)]
head(SACSUC_Index_Final)

#write.csv(SACSUC_Index_Final, "Output/SACSUC_Index_Final.csv", row.names = FALSE)
```

# Calculate Center of Distribution: Line 745

* Calculated using the months used to make the indices
* Formula taken from Sommer et al. 2011
* CD = sum(RiverKilo * CPUE)/sum(CPUE)
* Going to be used as response variable in model with flow/timing/temp as covariates (below)


* Could make this code much shorter - group by Region and year and calculate? It seems now we are using the station name to determine region. 
```{r}
SACSUC_RM <- 
  data_SACSUC_age0 %>% 
  left_join(Site_RM, 
            by = "StationCode") %>% 
  filter(CPUE != 0) # Removing records where CPUE was 0. This will prevent NAs in SJ when there were years w/ 0 catch (OW 0 CPUE shouldn't matter)

# Sacramento River
SACSUC_RM_Sac <-
  SACSUC_RM %>% 
  filter(grepl("SR", StationCode)) # Selecting stations that begin w/ SR
head(SACSUC_RM_Sac)

# SJ River
SACSUC_RM_SJ <-
  SACSUC_RM %>% 
  filter(grepl("SJ", StationCode)) # Selecting stations that begin w/ SJ
head(SACSUC_RM_SJ)

SACSUC_CDist_SAC <- 
  SACSUC_RM_Sac %>% 
  filter(Year %in% c(1995:2019)) %>% 
  group_by(Year) %>% 
  summarise(CDist_SAC = sum(RiverKilo * CPUE)/sum(CPUE))
head(SACSUC_CDist_SAC)

SACSUC_Month_CDist_SAC <- 
  SACSUC_RM_Sac %>% 
  filter(Year %in% c(1995:2019)) %>% 
  group_by(Year, 
           Month) %>% 
  summarise(CDist_SAC = sum(RiverKilo * CPUE)/sum(CPUE))
head(SACSUC_Month_CDist_SAC)

SACSUC_CDist_SJ <- 
  SACSUC_RM_SJ %>% 
  filter(Year %in% c(1995:2019)) %>% 
  group_by(Year) %>% 
  summarise(CDist_SJ = sum(RiverKilo * CPUE)/sum(CPUE))
head(SACSUC_CDist_SJ)

SACSUC_CDist <- 
  SACSUC_CDist_SAC %>% 
  left_join(SACSUC_CDist_SJ,
            by = "Year")
head(SACSUC_CDist)
```


